---
title: "Ravindra Raut's Resume"
author: Ravindra Raut
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/resume_styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(glue)
library(tidyverse)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')

# Load csv with position info
position_data <- read_csv('resume_positions.csv')
```


```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("
  <style>
  :root{
    --decorator-outer-offset-left: -6.5px;
  }
  </style>")
}
```


Aside
================================================================================

Contact {#contact}
--------------------------------------------------------------------------------

- <i class="fas fa-home"></i> Nanded, Maharashtra, India
- <i class='fa fa-phone'></i> (+91) 700 190 2565
- <i class='fa fa-envelope'></i> [raviraut206@gmail.com](raviraut206@gmail.com)
- <i class='fa fa-github'></i> [github.com/Ravindra-Raut](https://github.com/Ravindra-Raut/)
- <i class='fa fa-linkedin'></i> [ravindra-raut](https://www.linkedin.com/in/ravindra-raut-9402bb69/)
- <i class='fa fa-laptop'></i> [ravindra-raut.netlify.app](https://ravindra-raut.netlify.app/)

Programming {#skills}
--------------------------------------------------------------------------------
**Languages:** R, Python, Bash, PERL\
**Data visualization:** ggplot2, Plotly, IGV\
**Version control system:** Git and GitHub\
**Workflow management system:** Galaxy\
**Tools:** Rstudio, Pycharm, Visual Studio code\
**OS:** Linux (Ubuntu), MacOS\

Core competencies 
--------------------------------------------------------------------------------
Secondary and tertiary analysis of sequencing data: **Illumina**, **Oxford Nanopore**\

Databases: **RGAP**, **Ensembl**, **UCSC**, **Expasy**, **NCBI**, **HGVS**, **dbSNP**\

WGS: **FastQC**, **SPAdes**, **QUAST**, **PROKKA**\

RNA seq: **Trinity**, **RSEM**, **edgeR**, **Trinotate**\

Repeats analysis: **RepeatModeler**, **RepeatMasker**\

SSR mining: **MISA**, **GMATA**\

Variant calling: **GATK**, **BWA**,**VarScan**, **SnpEff**, **ClinVar**, **Mutalyze**, **VariantValidator**, **Ensembl VEP**\

Main
================================================================================

Ravindra Raut {#title}
--------------------------------------------------------------------------------
I am currently investigating the impact of transposable elements on the adaptation of the rice genome under fungal pathogen challenges and genome duplication. Experienced in using next-generation sequencing technologies like shotgun sequencing, linked reads, and long-read sequencing for whole-genome resequencing, variant calling, transcriptome assembly, differential expression analysis, and developing pipelines. Interested in working on next-generation approaches, solving complex problems relating to genomic plasticity and epigenetics.

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'education')
```



Research Experience {data-icon=flask}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'research_positions')
```

:::aside

Structural Bioinformatics
--------------------------------------------------------------------------------
structural databases: **PDB**\ 

Molecular docking: **AutoDock vina**\

Molecular simulation: **GROMACS**\

Homology modeling: **MODELLER**\

Genomics: **Bioconductor**\

Phylogenetic analysis: **MEGA**\

Digital image analysis: **ImageJ**, **Fiji**, **CellProfile**

:::


Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'teaching_positions')
```



Award and Honors {data-icon=medal}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'award_and_honors')
```


Talks, Poster Presenatation {data-icon=slideshare}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'talks_poster_presenatation')
```


Peer reviewed Publications {data-icon=book}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'peer_reviewed_publications')
```


:::aside
Certification {data-icon=certificate} 
--------------------------------------------------------------------------------
**Coursera**\
Bioconductor for Genomic Data Science\
Genomic Data Science with Galaxy\
Introduction to Genomic Technologies\
Introduction to Git and GitHub\
Data Visualization with Plotly Express\
Graphing with ggplot2\

**IBM**\
Data Visualization Using Python\
Data Visualization with R\

**Datacamp**\
Introduction to the Tidyverse\

:::

Volunteer Work {data-icon=group}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'volunteer_work')
```


:::aside

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown). 

The source code is available at [github.com/Ravindra-Raut/cv](https://github.com/Ravindra-Raut/cv).

See the full version of this CV with links at [ravindra-raut.netlify.app](https://ravindra-raut.netlify.app/cv).

Last updated on `r Sys.Date()`.

:::


```{r}
if(PDF_EXPORT){
  cat("
  
Links {data-icon=link}
--------------------------------------------------------------------------------

<br>


")
  
  walk2(links, 1:length(links), function(link, index){
    print(glue('{index}. {link}'))
  })
}
```


